---
title: "Crowding Significance Experiment SOP"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Interaction Buffer (Measured pH of 8.00)

2024 | 8 | 15 Last updated: `r Sys.Date()`

**Materials**

- 150 mM NaCl
- 25 mM Tris HCl, pH 8 (prepared from powdered form)
- Milli-Q water used for dilution

**Procedure**

**Solution A: 150 mM NaCl**

1. **Prepare NaCl Solution**: Start with a 2.5M NaCl stock solution.
2. **Dilute NaCl**: Measure 60 mL of the 2.5M NaCl stock and dilute it with 940 mL of Milli-Q water.
3. **Result**: You now have 1 liter of 150 mM NaCl solution.

**Solution B: 25 mM Tris HCl, pH 8**

4. **Prepare Tris HCl Solution**: Weigh out 3.94 g of Tris HCl powder.
5. **Dissolve and Dilute**: Add the Tris HCl powder to 1 liter of Milli-Q water and stir until fully dissolved.
6. **Result**: You now have 1 liter of 25 mM Tris HCl solution with a pH of 8. 

**Final Step: Interaction Buffer**

7. **Combine Solutions**: Mix Solution A (150 mM NaCl) with Solution B (25 mM Tris HCl).
8. **Final Product**: The resulting mixture is your interaction buffer.
6. You have made interaction buffer.


# 300 g/L, pH 7.0 Bovine Serum Albumin (BSA) Solution

2024 | 8 | 15 Last updated: `r Sys.Date()`

**Materials**

- Biotechnology Grade Albumin, Bovine (BSA) Fraction V 
- Interaction buffer (pH 8)

**Procedure**

1. Measure 7.5 g of BSA and pour it into a 125 mL Erlenmeyer flask.
2. Add the stirring bar to about 70 rpm into the Erlenmeyer flask. 
3. Slowly add about 10-20 mL of interaction buffer. DO NOT EXCEED OVER 25 mL!
4. Let stir until BSA is fully dissolved and in a homogenous mixture. (It can take a couple of hours to an entire day)
5. Pipette the dissolved BSA solution into the 25 mL volumetric flask, and pipette interaction buffer to the flask’s line.
6. BSA is ready to use! Store in the fridge otherwise.  
7. Measure pH, and make sure the BSA solution is STIRRING!

Note: Sodium azide is not used, so ensure BSA solution is used within the day! 


# Protein Purification

2024 | 8 | 15 Last updated: `r Sys.Date()`

**Expression and Purification**

The FRET pairs CyPet and YPet were cloned into pET28B for expression in BL21(DE3) after being N-terminally tagged to Ubc9 and the PCNA, respectively. For each gene, a BL21(DE3) cell line was inoculated 1:100, cultured at 37 °C to an OD of 0.6 at 600 nm, and then induced with 0.3 mM IPTG for an overnight period at 22 °C. After the cells were lysed with a sonicator using a lysis buffer (20 mM Tris-HCl (pH 7.4), 0.5 M NaCl, and 5 mM imidazole), they were centrifuged at 35,000× g. The soluble fraction was purified by 6×His tag to Ni-NTA beads affinity chromatography through a gravity column. The bound proteins were washed with Buffer 1 (20 mM Tris-HCl (pH 7.4), 0.3 M NaCl), Buffer 2 (20 mM Tris-HCl (pH 7.4), 1.5 M NaCl, and 0.5% Triton X-100), and Buffer 3 (20 mM Tris-HCl pH 7.4, 0.5 M NaCl, and 10 mM Imidazole). The proteins were eluted using the following Elution buffer (20 mM Tris-HCl, 200 mM NaCl, and 500 mM Imidazole) and dialyzed in 25 mM Tris-HCl (pH 8.0), 150 mM NaCl, and 1 mM DTT.



Sonicate the proteins for 10-15 min at 37°C 



# Statistical Analysis using a T-Test

2024 | 8 | 16 Last updated: `r Sys.Date()`


**Data**

```{r}
# Using data acquired from qFRET 
data_150g <- c(124.3, 541.9, 1318)
data_100g <- c(64.44, 40.12, 49.2)
data_50g  <- c(18.82, 22.03, 22.74)
data_0g   <- c(4.76, 5.699, 5.587)

```

**Welch Two Sample t-test between each group and the control group (0 g/L)**

**150 g/L vs 0 g/L**

```{r}
t_test_150_vs_0 <- t.test(data_150g, data_0g)
print(t_test_150_vs_0)

```

**100 g/L vs 0 g/L**

```{r}
t_test_100_vs_0 <- t.test(data_100g, data_0g)
print(t_test_100_vs_0)

```
**50 g/L vs 0 g/L**

```{r}
t_test_50_vs_0 <- t.test(data_50g, data_0g)
print(t_test_50_vs_0)

```
**Statistical Plot**

```{r}

# A library part of tidyverse 
library(ggplot2)

# Combining data into a data frame
data <- data.frame(
  Group = rep(c("150 g/L", "100 g/L", "50 g/L", "0 g/L"), each = 3),
  Value = c(data_150g, data_100g, data_50g, data_0g)
)

# Calculate means and standard deviations for each BSA Concentration
summary_stats <- aggregate(Value ~ Group, data, function(x) c(mean = mean(x), sd = sd(x)))
summary_stats <- do.call(data.frame, summary_stats)
summary_stats$Group <- factor(summary_stats$Group, levels = c("150 g/L", "100 g/L", "50 g/L", "0 g/L"))

# Perform T-tests and assign significance markers
t_test_150_vs_0 <- t.test(data_150g, data_0g)
t_test_100_vs_0 <- t.test(data_100g, data_0g)
t_test_50_vs_0 <- t.test(data_50g, data_0g)

# Adding significance markers based on p-values
summary_stats$Significance <- c(
  ifelse(t_test_150_vs_0$p.value < 0.001, "***",
         ifelse(t_test_150_vs_0$p.value < 0.01, "**",
                ifelse(t_test_150_vs_0$p.value < 0.05, "*", "ns"))),
  ifelse(t_test_100_vs_0$p.value < 0.001, "***",
         ifelse(t_test_100_vs_0$p.value < 0.01, "**",
                ifelse(t_test_100_vs_0$p.value < 0.05, "*", "ns"))),
  ifelse(t_test_50_vs_0$p.value < 0.001, "***",
         ifelse(t_test_50_vs_0$p.value < 0.01, "**",
                ifelse(t_test_50_vs_0$p.value < 0.05, "*", "ns"))),
  "ns"
)

# Plotting the data
ggplot(summary_stats, aes(x = Group, y = Value.mean)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.7) +
  geom_errorbar(aes(ymin = Value.mean - Value.sd, ymax = Value.mean + Value.sd), width = 0.2) +
  geom_text(aes(label = Significance), vjust = -0.5, size = 5) +  # Significance markers
  labs(title = "T-test: Mean Values with Standard Deviation for BSA Concentrations",
       x = "BSA Concentration (g/L)",
       y = "KD (μM)") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +  # Centering the title
  annotate("text", x = 3.5, y = max(summary_stats$Value.mean + summary_stats$Value.sd) * 1.2, 
           label = "Significance: * p < 0.05, ** p < 0.01, *** p < 0.001, ns: not significant",
           hjust = 1, size = 4)

```

**P value for 150 g/L to 0 g/L** 

```{r}
t_test_150_vs_0$p.value

```
**P value for 100 g/L to 0 g/L**

```{r}
t_test_100_vs_0$p.value

```
**P value for 50 g/L to 0 g/L**

```{r}
t_test_50_vs_0$p.value

```


